The Splashback Radius of Planck-SZ clusters

### 2018-09-24 Paper_new/RSP_paper_new.tex
Readding Paper_new

\begin{abstract}
We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.81_{-0.33}^{+0.28}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
both red and blue galaxy populations. The presence of the splashback radius in
color-separated galaxy distributions could potentially be used to put lower limits on the
quenching timescales for galaxies. Further, we record a strong increase 
in the fraction of red galaxies that is associated with the splashback radius.

@@

\citet{umetsu2017lensing} used Xray selected clusters to look for
the splashback radius using the weak lensing signal, however
stacking issues and the low signal-to-noise ratio remains a significant
hurdle. \citet{chang2017splashback} find evidence for the splashback
radius in the weak lensing signal, but their analysis was again done
using optically selected clusters in the Dark energy survey
\citep{dark2005dark}. Regardless of the projection issues present in
the optical cluster catalog, there is some inherent circularity
present in the logic of using photometric galaxies to select
clusters as over-densities in a given aperture, and then using the
same photometric sample of galaxies to look for the splashback
radius. There is a possibility that the aperture used to select the
cluster catalogs could be imprinted in a non-trivial way on the
measured number density profiles of clusters.

@@

Given that the splashback radius represents a true halo boundary,
the observations of the splashback radius can be used to study a
variety of galaxy formation questions. Such as questions 
regarding the timescales and the spatial scales within
which star forming galaxies quench after they fall into the cluster
potential. Answers to those questions are important to understand 
the evolution of satellite galaxies in massive galaxy clusters. 
If blue galaxies quench before
they complete a single orbit, then they are not expected to show a
splashback feature in their density distribution. In pursuit of this
question, we also explore the dependence of the cluster-galaxy
cross-correlations separately for the red and blue galaxies and
explore their relative contributions to the overall density profile.

@@

for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ is

@@

    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal & Normal & Normal\\ 

@@

    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ & $0.15 | 0.21$ & $0.41 | 0.3$\\

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
in order to mimic the redshift range used by
\citet{more2016detection}. Due to the large beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
include the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Section~\ref{sec:mis-centering}). 
The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. The sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

@@

For the visual inspection and centering of the clusters, we use the
Pan-Starrs $gri$ \textit{stack} images around each cluster position.
The galaxy catalog is obtained from the  \textit{StackObjectThin}
table, which is publicly available on the \fnurl{\textit{Barbara A.
Mikulski Archive for Space Telescopes}
(MAST)}{http://archive.stsci.edu/}. To select only objects detected
with acceptable precision we restrict our search to those objects
which have been flagged as \textit{BestDetection}s. We further
restrict the catalog to objects flagged as
\textit{PrimaryDetection}s in order to select unique objects. This
is necessary since the survey is divided into overlapping
\textit{projectioncells} and \textit{skycells}.

@@

We use the functional form of \citet{diemer2014dependence} in order
to model our two-dimensional correlation function measurements. This
functional form consists of an inner Einasto profile and an outer
power law profile connected by a smooth transition
\begin{align}
\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
\label{eq:dk14}
\end{align}
where $r$ indicates the three-dimensional radial distance from the
halo center \citep{diemer2014dependence}. We model the
two-dimensional correlation function, $\xi_{\rm 2D}$ as an integral
over the three-dimensional correlation function
\begin{equation}
\xi_{\rm (2D,0)}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
\label{eq:surface}
\end{equation}
where we adopt $R_{\mathrm{max}}=40$ $h^{-1}$Mpc for the maximum projection
length. Variations of this length do not change the location of the
splashback radius appreciably as tested in
\citet{more2016detection}. The functional form adopted in
Equation~\ref{eq:dk14} has nine model parameters,
$\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
\rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and
$\gamma$. Given the perfect degeneracy between the parameters
$r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
h^{-1}$Mpc.

\paragraph{Modelling cluster mis-centering}
\label{sec:mis-centering}
Mis-centering of the central cluster positions can heavily affect 
the small-scale correlation function on scales smaller than the typical mis-centering distance. 
Although, the splashback radius is located at much larger scales, 
the change of the inner part of the correlation function can alter the model fit significantly. Mis-centering effects are not expected to change the location of the splashback feature but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.

Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
the correlation function $\xi_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
unaffected by mis-centering $\xi_{\rm (2D,0)}(R)$ by

\begin{equation} 
\xi_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm (2D,0)}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
\label{eq:full}
\end{equation}

where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
relates to the unaffected correlation function $\xi_{\rm (2D,0)}$ as

\begin{equation}
\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm (2D,0)}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
\end{equation}

Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
of the mis-centering probability distribution $\sigma$.
\newline

We cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
two samples. The central values as well as the scales of the priors are listed in Table~\ref{tab:priors}.

Including mis-centering our model is described by ten model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function affected by mis-centering to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

@@

\subsection{Separation of red and blue galaxies}
\label{sec:Color}

We are also interested in measuring the cluster-galaxy
cross-correlations for the blue and the red galaxy samples
separately. We use a $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut
which varies with the redshift of the clusters in order to account
for the k-corrections, which cannot be computed individually for
each galaxy. We regard a galaxy as red if
$g_{\mathrm{P1}}-r_{\mathrm{P1}} > 0.65 + 3.04$ $(z_{\mathrm{clu}} -
0.1)$ and as blue otherwise. Depending upon the cluster redshift
under consideration the same galaxy may be considered red or blue. Our
method avoids the use of uncertain photometric redshifts to derive
k-corrections \citep[cf.][]{baxter2017halo}. We will study the
cross-correlations to derive the splashback radii for these galaxy
populations separately, as well as the fractional
contributions of the red and the blue galaxies to the total density profile
as a function of radius.

@@

We fit these measurements with our parametric model in Equation~\ref{eq:full}
and compute the posterior distribution of the model parameters 
as described in Section~\ref{sec:estimators}. The
median of the MCMC fit is indicated by the central solid line, while
the shaded area marks the 68\% credible interval for the fit. The
median values of the posterior distributions of the parameters along
with their 68\% confidence intervals are listed in
Table~\ref{tab:fit_parameters} along with their minimal, reduced
$\chi^2$ values. The two-dimensional posterior distributions for
each pair of parameters are shown in Figures~\ref{fig:corner_21},
\ref{fig:corner_21.5} and \ref{fig:corner_22} for the three absolute
magnitude limits, respectively.

\begin{figure}
    \includegraphics[scale=0.65]{2D_graphs.pdf}
\caption{The estimates of the two-dimensional cross-correlation
signals (black dots) are shown in the left column. The colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The magnitude limit applied to the galaxy
catalog is indicated in each row along with the signal-to-noise ratio (SNR). 
The vertical, shaded regions indicate the estimates of the locations of 
steepest slope of the profiles as estimated from the corresponding minima of the
derivative profiles, which are shown in the right column. For
comparison, the location of the $r_{\mathrm{200m}}$ radius as
calculated from the average cluster sample properties is indicated
by the black, dotted lines.}
   \label{fig:2D_graphs}
\end{figure}

\begin{figure}
    \includegraphics[scale=0.65]{3D_graphs.pdf}
\caption{The estimates of the three-dimensional cross-correlation
signals are shown in the left column. The colored curves show the
model fits of the functional form in Equation~\ref{eq:model}. The magnitude
limit applied on the galaxy catalog is indicated in each row along with 
the signal-to-noise ratio (SNR). The vertical, shaded regions indicate the 
estimates of the splashback radii as estimated from the corresponding minima 
of the derivative profiles, which are shown in the right column. For comparison, 
the location of the $r_{\mathrm{200m}}$ radius as calculated from the
average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:3D_graphs} 
\end{figure}

\begin{table}
    \centering
    \caption{We list the signal to noise ratios (SNRs) of our
different estimates of the two-dimensional cross-correlation
obtained by using the different galaxy samples. For comparison: The SNR
achieved by \citet{more2016detection} is 263.0. It is much higher
due to size of the cluster sample used in their study.}
    \label{tab:snr}
    \begin{tabular}{cccc}
    \hline
    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
    \hline
    \hline
   SNR & 42.4 & 43.3 & 30.9 \\
    \hline
    \end{tabular} 
\end{table}

\begin{table*}
    \centering
    \caption{We list our findings for the fitting parameters obtained from cross-correlating the galaxy cluster sample with the different galaxy catalogs. For each parameter estimate the median as well as the 16\% and 84\% quantiles of the posterior distribution are given. We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$) as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$). In the last column the minimal, reduced $\chi^2$ value of the model fit is indicated. The two-dimensional posterior distributions of the fitting parameters are displayed in 
Figure~\ref{fig:corner_21} up to Figure~\ref{fig:cornerblue}.}
    \label{tab:fit_parameters}
    \begin{tabular}{cccccccccccccc}
    \hline 
gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\rm sp}^{\rm 2D}$& $r_{\rm sp}^{\rm 3D}$& $\chi^2/\nu$ \\
\hline 
\hline 
PS 21 & $-0.92_{-0.56}^{+0.50}$ & $-1.19_{-0.21}^{+0.22}$ & $0.31_{-0.26}^{+0.29}$ & $0.0130_{-0.0083}^{+0.0062}$ & $0.72_{-0.22}^{+0.27}$ & $0.103_{-0.110}^{+0.056}$ & $0.85_{-0.36}^{+0.27}$ & $0.28_{-0.19}^{+0.12}$ & $1.35_{-0.12}^{+0.13}$ & $1.76_{-0.33}^{+0.29}$ & $0.511$ \\
\hline
PS 21.5 & $-0.91_{-0.48}^{+0.51}$ & $-0.98_{-0.18}^{+0.16}$ & $0.28_{-0.28}^{+0.26}$ & $0.0084_{-0.0060}^{+0.0041}$ & $0.53_{-0.23}^{+0.27}$ & $0.086_{-0.112}^{+0.051}$ & $0.78_{-0.34}^{+0.26}$ & $0.25_{-0.18}^{+0.12}$ & $1.30_{-0.10}^{+0.10}$ & $1.81_{-0.33}^{+0.28}$ & $0.178$ \\
\hline
PS 22 & $-0.99_{-0.46}^{+0.49}$ & $-0.90_{-0.17}^{+0.16}$ & $0.27_{-0.27}^{+0.26}$ & $0.0058_{-0.0052}^{+0.0027}$ & $0.43_{-0.29}^{+0.26}$ & $0.114_{-0.252}^{+0.076}$ & $0.71_{-0.38}^{+0.27}$ & $0.27_{-0.33}^{+0.16}$ & $1.33_{-0.17}^{+0.13}$ & $1.96_{-0.45}^{+0.37}$ & $0.264$ \\
\hline 
PS 21.5 (R) & $0.17_{-0.50}^{+1.03}$ & $-0.95_{-0.34}^{+0.44}$ & $-0.21_{-0.56}^{+0.26}$ & $0.0073_{-0.0084}^{+0.0040}$ & $0.59_{-0.38}^{+0.34}$ & $0.18_{-0.35}^{+0.22}$ & $0.52_{-0.41}^{+0.26}$ & $0.29_{-0.32}^{+0.23}$ & $1.20_{-0.12}^{+0.14}$ & $2.03_{-0.38}^{+0.38}$ & $1.194$ \\
\hline
PS 21.5 (B) & $-0.83_{-0.44}^{+0.49}$ & $-0.71_{-0.18}^{+0.19}$ & $0.24_{-0.30}^{+0.26}$ & $0.0112_{-0.0062}^{+0.0048}$ & $0.63_{-0.18}^{+0.23}$ & $0.28_{-0.20}^{+0.14}$ & $0.55_{-0.25}^{+0.16}$ & $0.44_{-0.33}^{+0.25}$ & $1.53_{-0.13}^{+0.13}$ & $2.30_{-0.23}^{+0.24}$ & $0.603$ \\
\hline
    \end{tabular} 
\end{table*}

>>>>

\begin{abstract}
We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
both red and blue galaxy populations. The presence of the splashback radius in
color-separated galaxy distributions could potentially be used to put lower limits on the
quenching timescales for galaxies. Further, we record an increase 
in the fraction of red galaxies that is associated with the splashback radius.

@@

\citet{umetsu2017lensing} used Xray selected clusters to look for
the splashback radius using the weak lensing signal, however
stacking issues and the low signal-to-noise ratio remains a significant
hurdle. \citet{chang2017splashback} found evidence for the splashback
radius in the weak lensing signal, but their analysis was again done
using optically selected clusters in the Dark energy survey
\citep{dark2005dark}. Regardless of the projection issues present in
the optical cluster catalog, there is some inherent circularity
present in the logic of using photometric galaxies to select
clusters as over-densities in a given aperture, and then using the
same photometric sample of galaxies to look for the splashback
radius. There is a possibility that the aperture used to select the
cluster catalogs could be imprinted in a non-trivial way on the
measured number density profiles of clusters.

@@

Given that the splashback radius represents a true halo boundary,
the observations of the splashback radius can be used to study a
variety of galaxy formation questions. Such as questions 
regarding the timescales and the spatial scales within
which star forming galaxies quench after they fall into the cluster
potential. Answers to those questions are important to understand 
the evolution of satellite galaxies in massive galaxy clusters. 
If blue galaxies quench before
they complete a single orbit, then they are not expected to show a
splashback feature in their density distribution. In pursuit of this
question, we also explore the dependence of the cluster-galaxy
cross-correlations separately for the red and blue galaxy populations 
and explore their relative contributions to the overall density profile.

@@

for the splashback radii $r^{\mathrm{3D,theo}}_{\mathrm{sp}}$ are

@@

    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 

@@

    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ \\

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
in order to mimic the redshift range used by
\citet{more2016detection}. Due to the large beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
study the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Appendix~\ref{sec:mis-centering}).

The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. A map of the sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

@@

For the visual inspection and centering of the clusters, we use the
Pan-Starrs $gri$ \textit{stack} images around each cluster position.
The galaxy catalog is obtained from the  \textit{StackObjectThin}
table, which is publicly available on the \fnurl{\textit{Barbara A.
Mikulski Archive for Space Telescopes}
(MAST)}{http://archive.stsci.edu/}. To select only objects detected
with acceptable precision we restrict our search to those objects
which have been flagged as \textit{BestDetection}s. We further
restrict the catalog to objects flagged as
\textit{PrimaryDetection}s in order to select unique objects. This
is necessary since the survey is divided into overlapping
\textit{projectioncells} and \textit{skycells}, which causes some objects
to be listed multiple times.

@@

We use the functional form of \citet{diemer2014dependence} in order
to model our two-dimensional correlation function measurements. This
functional form consists of an inner Einasto profile and an outer
power law profile connected by a smooth transition
\begin{align}
\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \label{eq:model} \\
\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\\
f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
\label{eq:dk14}
\end{align}
where $r$ indicates the three-dimensional radial distance from the
halo center \citep{diemer2014dependence}. We model the
two-dimensional correlation function, $\xi_{\rm 2D}$ as an integral
over the three-dimensional correlation function
\begin{equation}
\xi_{\rm 2D}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
\label{eq:surface}
\end{equation}
where we adopt $R_{\mathrm{max}}=40$ $h^{-1}$Mpc for the maximum projection
length. Variations of this length do not change the location of the
splashback radius appreciably as tested in
\citet{more2016detection}. The functional form adopted in
Equation~\ref{eq:surface} has nine model parameters,
$\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
\rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and
$\gamma$. Given the perfect degeneracy between the parameters
$r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
h^{-1}$Mpc.

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

@@

Mis-centering of the central cluster positions can heavily affect 
the small-scale correlation function on scales smaller than the typical mis-centering distance. 
Although, the splashback radius is located at much larger scales, 
the change of the inner part of the correlation function can alter the model fit significantly. 
Mis-centering effects are not expected to change the location of the splashback feature 
but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.
We discuss the modelling of mis-centering and its effects on the inferred splashback radii in Appendix~\ref{sec:mis-centering}.
\subsection{Separation of red and blue galaxies}
\label{sec:Color}

We are also interested in measuring the cluster-galaxy
cross-correlations for the blue and the red galaxy samples
separately. We use a $g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut
which varies with the redshift of the clusters in order to account
for the k-corrections, which cannot be computed individually for
each galaxy.

We exploit the XXX SDSS galaxy sample to calibrate our color cut (cite ???).
The SDSS galaxy sample is divided into a red and a blue galaxy population
using the color cut XXX (cite???). By cross matching the sample with our Pan-STARRS
catalog we can identify parts of the Pan-STARRS galaxies as red and blue galaxies,
respectively. Additionally, we assign the photometric redshifts from the SDSS sample to
the matched Pan-STARRS galaxies. The redshift dependent 
$g_{\mathrm{P1}}-r_{\mathrm{P1}}$ color cut is then calibrated to exclude
red galaxies from being characterized as blue galaxies at a confidence level of 3$\sigma$.

Depending upon the cluster redshift
under consideration the same galaxy may be considered red or blue. Our
method avoids the use of uncertain photometric redshifts to derive
k-corrections \citep[cf.][]{baxter2017halo}. We will study the
cross-correlations to derive the splashback radii for these galaxy
populations separately, as well as the fractional
contributions of the red and the blue galaxies to the total density profile
as a function of radius.

@@

We fit these measurements with our parametric model in Equation~\ref{eq:surface}
and compute the posterior distribution of the model parameters 
as described in Section~\ref{sec:estimators}. The
median of the MCMC fit is indicated by the central solid line, while
the shaded area marks the 68\% credible interval for the fit. The
median values of the posterior distributions of the parameters along
with their 68\% confidence intervals are listed in
Table~\ref{tab:fit_parameters} along with their minimal, reduced
$\chi^2$ values. The two-dimensional posterior distributions for
each pair of parameters are shown in Figures~\ref{fig:corner_21},
\ref{fig:corner_21.5} and \ref{fig:corner_22} for the three absolute
magnitude limits, respectively.

\begin{figure}
    \includegraphics[scale=0.65]{2D_graphs_with_spline_no_mc.pdf}
\caption{The estimates of the two-dimensional cross-correlation
signals (black dots) are shown in the left column. The colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The magnitude limit applied to the galaxy
catalog is indicated in each row along with the signal-to-noise ratio (SNR). 
The vertical, shaded regions indicate the estimates of the locations of 
steepest slope of the profiles as estimated from the corresponding minima of the
derivative profiles, which are shown in the right column. For
comparison, the location of the $r_{\mathrm{200m}}$ radius as
calculated from the average cluster sample properties is indicated
by the black, dotted lines.}
   \label{fig:2D_graphs}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[scale=0.85]{3D_graphs_with_spline_no_mc.pdf}
\caption{The estimates of the three-dimensional cross-correlation
signals are shown in the leftmost column. The colored curves show the
model fits of the functional form in Equation~\ref{eq:model}. The magnitude
limit applied on the galaxy catalog is indicated in each row along with 
the signal-to-noise ratio (SNR). The vertical, shaded regions indicate the 
estimates of the splashback radii as estimated from the corresponding minima 
of the derivative profiles, which are shown in the column in the middle. The
rightmost column shows the second derivative profiles in matching color.
For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated 
from the average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:3D_graphs} 
\end{figure*}

\begin{table}
    \centering
    \caption{We list the signal to noise ratios (SNRs) of our
different estimates of the two-dimensional cross-correlation
obtained by using the different galaxy samples. For comparison: The SNR
achieved by \citet{more2016detection} is 263. It is much higher
due to size of the cluster sample used in their study.}
    \label{tab:snr}
    \begin{tabular}{cccc}
    \hline
    gal cat & PS 21 & PS 21.5 & PS 22 \\ 
    \hline
    \hline
   SNR & 42.4 & 43.3 & 30.9 \\
    \hline
    \end{tabular} 
\end{table}

\begin{table*}
    \centering
    \caption{We list our findings for the fitting parameters obtained from cross-correlating the galaxy cluster sample with the different galaxy catalogs. For each parameter estimate the median as well as the 16\% and 84\% quantiles of the posterior distribution are given. We also list the estimated locations of the steepening feature in the two-dimensional cross-correlation signal ($R_{\mathrm{sp}}^{\mathrm{2D}}$) as well as the three-dimensional splashback radius ($r_{\mathrm{sp}}^{\mathrm{3D}}$). In the last column the minimal, reduced $\chi^2$ value of the model fit is indicated. The two-dimensional posterior distributions of the fitting parameters are displayed in 
Figure~\ref{fig:corner_21} up to Figure~\ref{fig:cornerblue}.}
    \label{tab:fit_parameters}
    \begin{tabular}{cccccccccccccc}
    \hline 
gal cat & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_{\mathrm{0}}$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $R_{\mathrm{sp}}^{\mathrm{2D}}$ & $r_{\mathrm{sp}}^{\mathrm{3D}}$ & $\chi^2/\nu$ \\
\hline 
\hline 
PS 21 & $-2.93_{-0.50}^{+0.44}$ & $-1.06_{-0.18}^{+0.14}$ & $0.35_{-0.24}^{+0.27}$ & $0.000179_{-0.000086}^{+0.000075}$ & $0.78_{-0.19}^{+0.24}$ & $0.123_{-0.122}^{+0.051}$ & $0.74_{-0.31}^{+0.21}$ & $0.35_{-0.21}^{+0.13}$ &$1.384_{-0.096}^{+0.088}$&$1.86_{-0.26}^{+0.25}$& $1.524$ \\
\hline
PS 21.5 & $-2.93_{-0.45}^{+0.45}$ & $-0.95_{-0.16}^{+0.13}$ & $0.32_{-0.25}^{+0.25}$ & $0.000103_{-0.000065}^{+0.000047}$ & $0.56_{-0.22}^{+0.25}$ & $0.095_{-0.115}^{+0.045}$ & $0.74_{-0.32}^{+0.24}$ & $0.27_{-0.19}^{+0.12}$ &$1.323_{-0.086}^{+0.080}$&$1.85_{-0.30}^{+0.26}$& $0.285$ \\
\hline
PS 22 & $-2.95_{-0.44}^{+0.49}$ & $-0.91_{-0.17}^{+0.14}$ & $0.28_{-0.27}^{+0.25}$ & $0.000062_{-0.000051}^{+0.000028}$ & $0.41_{-0.28}^{+0.25}$ & $0.094_{-0.190}^{+0.060}$ & $0.76_{-0.36}^{+0.29}$ & $0.24_{-0.27}^{+0.14}$ &$1.31_{-0.14}^{+0.11}$&$1.90_{-0.40}^{+0.32} $&$0.211$ \\
\hline
PS 21.5 (R) & $-0.69_{-0.54}^{+0.55}$ & $-0.99_{-0.20}^{+0.17}$ & $0.24_{-0.31}^{+0.30}$ & $0.0092_{-0.0065}^{+0.0046}$ & $0.63_{-0.27}^{+0.30}$ & $0.157_{-0.171}^{+0.091}$ & $0.54_{-0.20}^{+0.16}$ & $0.36_{-0.26}^{+0.17}$ & $1.437_{-0.089}^{+0.099}$ & $2.13_{-0.21}^{+0.22}$ & $0.502$ \\
\hline
PS 21.5 (B) & $-1.00_{-0.24}^{+0.47}$ & $-0.31_{-0.15}^{+0.21}$ & $0.22_{-0.31}^{+0.19}$ & $0.0078_{-0.0047}^{+0.0036}$ & $0.52_{-0.21}^{+0.24}$ & $0.31_{-0.27}^{+0.29}$ & $0.61_{-0.44}^{+0.31}$ & $0.30_{-0.39}^{+0.29}$ & $1.43_{-0.13}^{+0.12}$ & $2.34_{-0.34}^{+0.33}$ & $1.355$ \\
\hline
    \end{tabular} 
\end{table*}
